Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-01 Rapport/Article/Article.tex
Simulation 01 06/01/2019

@@

%\subsection{Notation}
%Special notations used throughout the paper as shown in figures tac tac

@@

% TODO: WRITE WHICH ACTIVATION FUNCTION I WILL USE
%

@@

\begin{comment}
\subsection{Autoencoders}
TO PARAPHRASE: The parallel computing
capabilities of NNs allow us to solve or, at least, approximate
the MLD problem in polynomial time [7]. Moreover, the
weights of the NN are precomputed during training and the
decoding step itself is then relatively simple.

@@

\end{comment}
%\section{Procedure and methods}
%Explain what I Should do to achieve my goal
\begin{comment}

@@

>>>>

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/test}
    \caption{Diagram of a simplified communication system.}\label{fig:cs}
\end{figure}

@@

\subsection{Notation}
Special notations used throughout the paper as shown in figures tac tac

@@

% TODO: WRITE WHICH ACTIVATION FUNCTION I WILL USE
%
Two common activation functions are the rectified linear unit (ReLU) and the sigmoid function. Both will be applied in the NN treated in this paper. Their mathematical expressions are shown below.

\begin{align}
	\text{ReLU: } \sigma_1 (x)& = max\{0, x\} \label{eq:relu}\\ 
	\text{Sigmoid: } \sigma_2 (x)& = \frac{1}{1+e^{- \lambda x}} \label{eq:sig}
\end{align}
where $x \in \mathbb{R}$.

@@

\subsection{Autoencoders}
TO PARAPHRASE: The parallel computing
capabilities of NNs allow us to solve or, at least, approximate
the MLD problem in polynomial time [7]. Moreover, the
weights of the NN are precomputed during training and the
decoding step itself is then relatively simple.

@@

\section{Procedure and Methodology}
Explain what I Should do to achieve my goal
Talk about decoder + autoencoder and the OBJECTIVE of each one, G matrix of choice, Batch size, The reader should be able to replicate what I ve done

\subsection{Array Decoder}
Architecture, Training parameters, cite choice of p train \cite{b13}, number of epochs, Talk about noise layer and its removal in prediction,

\subsection{One-hot Decoder}
Architecture, Training parameters, Explain what is a One hot decoding, talk about the matrix transformation from one hot to messages, p train equals 0, number of epochs

\subsection{Autoencoder}
Architecture, Training and simulation parameters, procedure to find a M epoch suitable, choices of p train, Talk about NN separation,

\section{Results and Analysis}

\subsection{Decoders}
BER Curves from both decoders, analyse why the number of epochs is so different.

\subsection{Autoencoder}
BER Curves of simulation varying p, best choice of p, analyse autoencoder with best choice of p

\subsection{Decoding time analysis}
compare time in decoding between map, autoencoder and a decoder.

\section{Conclusions}

\begin{comment}

@@

\bibitem{b13} M. Benammar and P. Piantanida, “Optimal training channel statistics for neural-based decoders,” in Asilomar, Oct 2018, pp. 2157–2161.
